---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BertopicR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of BertopicR is to allow R users to access bertopic's topic modelling suite in R. The package does not aim to implement every feature of bertopic, you may  submit issues for feature requests; however,it may be faster to go direct to the original, Python library which has excellent documentation. [[BERTopic documentation](https://maartengr.github.io/BERTopic/index.html)]

The package currently installs an exact version of bertopic - 0.15.0, this should make it easier to maintain the package over time and prevent new users from running into install errors.


## Installation

Before installing bertopic make sure that you have miniconda installed, if you don't:
```{r, eval=FALSE}
library(reticulate) #install.packages("reticulate") if you don't have this already or aren't sure how to install.

reticulate::install_miniconda()
```


Once you have reticulate and miniconda installed, you can then install the development version of BertopicR from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jpcompartir/BertopicR")

library(BertopicR)

#Check your environment has been loaded correctly and bertopic has been installed:
BertopicR::check_python_dependencies()
```

If you receive the message:
"bertopic not in installed packages of current environment..."
run:
```{r, eval = FALSE}
BertopicR::install_python_dependencies()
```

## Example

```{r}
#TODO
```

