---
title: "Testing The Pipeline"
author: "Jack Penzer"
date: "2023-07-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We've noticed some discrepancies between the output of the topic modelling process when run in Python vs when run in R.

```{r}
library(BertopicR)
library(dplyr)
library(tidyr)
library(readr)
library(dplyr)
```

Read in the original data and embeddings:
```{r}
data <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/642_644_search_engine_ai_chatbot/644_phase_2/data/helper_data/644_for_colab.csv")
data_umapped <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/642_644_search_engine_ai_chatbot/644_phase_2/data/helper_data/644_embeddings_umap_joined.csv")
embeddings <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/642_644_search_engine_ai_chatbot/644_phase_2/data/helper_data/644_umap_embeddings.csv")
```


```{r}
docs <- data$clean_text
embeddings <- embeddings[,-1]
```

# Reducing

```{r}
reducer <- bt_make_reducer(min_dist = 0.1)
reduced_embeddings <- bt_do_reducing(reducer, embeddings)
reducer$get_params # Check the reducer params against colab

reducer_high_mem <- bt_make_reducer(min_dist = 0.1, low_memory = FALSE)
reducer_high_mem$get_params()
high_mem_reduced_embeddings <- bt_do_reducing(reducer_high_mem, embeddings)
```

## Low memory reducing two
```{r}
reducer_low_mem_two <- bt_make_reducer(min_dist = 0.1)
reducer_low_mem_two$low_memory == TRUE
reduced_embeddings_low_mem_two <- bt_do_reducing(reducer_low_mem_two, embeddings)
```
Compare the reduced embeddings and reduced embeddings 2
```{r}
if(all(reduced_embeddings_low_mem_two == reduced_embeddings)){
  print("This is TRUE and it should've been TRUE")
} else{ 
  print("***This is FALSE and it should've been TRUE***")}
```
The UMAPPing is not deterministic either, when the right params are set.

# Clustering
Dictionary of params from Colab for clusterer:
{'algorithm': 'best',
 'allow_single_cluster': False,
 'alpha': 1.0,
 'approx_min_span_tree': True,
 'cluster_selection_epsilon': 0.0,
 'cluster_selection_method': 'eom',
 'core_dist_n_jobs': 4,
 'gen_min_span_tree': True,
 'leaf_size': 40,
 'match_reference_implementation': False,
 'max_cluster_size': 0,
 'memory': Memory(location=None),
 'metric': 'euclidean',
 'min_cluster_size': 400,
 'min_samples': 100,
 'p': None,
 'prediction_data': True}
 
 $algorithm [1] "best"
$allow_single_cluster [1] FALSE
$alpha [1] 1
$approx_min_span_tree [1] TRUE
$cluster_selection_epsilon [1] 0
$cluster_selection_method [1] "eom"
$core_dist_n_jobs [1] 4
$gen_min_span_tree [1] TRUE
$leaf_size [1] 40
$match_reference_implementation [1] FALSE
$max_cluster_size [1] 0
$memory Memory(location=None)
$metric [1] "euclidean"
$min_cluster_size [1] 400
$min_samples [1] 100
$p NULL
$prediction_data [1] TRUE

```{r}
clusterer <- bt_make_clusterer_hdbscan(min_cluster_size = 400L, min_samples = 100L, metric = "euclidean", prediction_data = TRUE, gen_min_span_tree = TRUE)

# clusterer$probabilities_ # should error
```

```{r}
clusters_low_mem <- bt_do_clustering(clustering_model = clusterer, reduced_embeddings)

clusters_low_mem_two <- bt_do_clustering(clustering_model = clusterer, reduced_embeddings)

if(all(clusters_low_mem == clusters_low_mem_two)){
  print("This is TRUE and it should've been TRUE")
} else {
  print("***This is FALSE and it should've been TRUE***")
}
```



```{r}
high_mem_clusters <- bt_do_clustering(clusterer, high_mem_reduced_embeddings)
```

```{r}
high_mem_clusters_two <- bt_do_clustering(clusterer, high_mem_reduced_embeddings)
```

#Seems like hdbscan definitely is deterministic
```{r}
if(all(high_mem_clusters_two == high_mem_clusters)){
  print("This is TRUE and it should've been TRUE")
} else{
  print("***This is FALSE and it should've been TRUE***")
}
```


# Does the hdbscan clustering algorithm give the same output for both of the reduced embeddings?

```{r}
clusters_low_mem #made with 
clusters_low_mem_reducer_two <- bt_do_clustering(clusterer, reduced_embeddings_low_mem_two)

if(all(clusters_low_mem == clusters_low_mem_reducer_two)){
  print("This is TRUE and it should've been TRUE")
} else {
  print("***This is FALSE and it should've been TRUE***")
}
```

```{r}
if(all(high_mem_reduced_embeddings == reduced_embeddings)){
  print("***This is TRUE and it should've been FALSE***")
} else{
  print("This is FALSE and it should've been FALSE")
}
```

# How different are the low memory and high memory embeddings?

```{r}
reduced_embeddings <- reduced_embeddings %>%
  as_tibble()
high_mem_reduced_embeddings <- high_mem_reduced_embeddings  %>%
  as_tibble()

names(high_mem_reduced_embeddings) <- stringr::str_replace(names(high_mem_reduced_embeddings), "V", "X")

bind_cols(high_mem_reduced_embeddings, reduced_embeddings)

differences <- purrr::map2_dfr(high_mem_reduced_embeddings, reduced_embeddings, ~ .x - .y)

absolute_differences <- differences %>%
  mutate(across( everything(), abs))

absolute_differences <- absolute_differences %>%
  mutate(row_total = rowSums(.)) %>%
  mutate(document = row_number())


absolute_differences %>%
  mutate(group = document %/% 10000) %>%
  summarise(mean_diff = mean(row_total), median_diff = median(row_total), max_diff = max(row_total), .by = group) #no notieceable difference in the order the reduced embeddings were calculated

#Check if there's a difference if the groups are arrange differently?
absolute_differences %>%
  mutate(group = document %% 10) %>%
  summarise(mean_diff = mean(row_total), median_diff = median(row_total), max_diff = max(row_total), .by = group)
```

Can't find a difference between groups meaningfully. Seems like it's just that the floating points are so different, but why does this have such a big effect on the clustering?


```{r}
clusterer_min_10 <- bt_make_clusterer_hdbscan(prediction_data = TRUE, gen_min_span_tree = TRUE)

cluster10_reduced_low_mem <- bt_do_clustering(clusterer_min_10, reduced_embeddings)
cluster10_reduced_high_mem <- bt_do_clustering(clusterer_min_10, high_mem_reduced_embeddings)
```

```{r}
length(unique(cluster10_reduced_low_mem)) # 626 clusters
length(unique(cluster10_reduced_high_mem)) #640 clusters
length(unique(clusters_low_mem)) #4
length(unique(high_mem_clusters)) #25

clusterer_min_10$get_params()
```

```{r}

```

