---
title: "representation_c_distributed"
output: html_document
---

```{r}
library(tidyverse)
library(BertopicR)
library(reticulate)
library(testthat)


Sys.setenv("TOKENIZERS_PARALLELISM" = "0")
# reticulate::py_run_string("import torch; torch.cuda.is_available = lambda: False; torch.backends.mps.is_available = lambda: False")
```

```{r}
jack_packages <- py_list_packages(envname = "BertopicR") |>  as_tibble()
# jack_packages |> write_csv("~/Downloads/jack_bt_packages.csv")
aoife_packages <- read_csv("~/Downloads/aoife_bt_packages.csv")
# reticulate::py_install("accelerate=0.23.0") # remove this later
# reticulate::py_inst
```

```{r}
aoife_packages |>  
  filter(!package %in% jack_packages$package) |> 
  as.data.frame()
```

```{r}
package_pattern <- "torch|transfor|bertop|hugging|dataset|tqdm|scipy"
aoife_packages |>  filter(grepl(package_pattern, package))
jack_packages |> filter(grepl(package_pattern, package))
# jack_packages |> select(package) |>  as.data.frame()

```

Iteratively removing all of these packages and making sure versions align:

Can get past the previous error (about torch.\_C.) when we have the same versions of pytorch, torchvision, transformers. Then we get a wandb error, but that looks like it comes from elsewhere. Maybe datasets different versions? But then we can't install because of tqdm, so we remove tqdm and align versions

```{r}
conda_remove("BertopicR", c("pytorch", "torchvision"))
conda_remove("BertopicR", c("transformers"))
conda_remove("BertopicR", "transformers")
conda_remove("BertopicR", "huggingface_hub")
py_install(
  packages = c("torch==2.0.1", "pytorch-revgrad==0.2.0"),
  pip = TRUE
)
conda_remove("BertopicR", "datasets")
conda_remove("BertopicR", "tqdm")
```

Then installing matching versions

```{r}
# py_install(
#   packages = c("transformers==4.30.2")
# )
# py_install(envname = "BertopicR", packages = "bertopic==0.15.0")
# py_install(envname = "BertopicR", packages = c("transformers==4.30.2"), pip = TRUE)
# py_install(envname = "BertopicR", packages = c("spacy-transformers==1.2.5", "transformer-smaller-training-vocab==0.3.2"), pip = TRUE)
# py_install(envname = "BertopicR", "torchvision==0.15.2")
# py_install(envname = "BertopicR", "huggingface_hub==0.16.4")
```

This combination actually works:

```{r}
py_install(envname = "BertopicR", packages = c("pytorch-revgrad==0.2.0","torch==2.0.1", "transformers==4.30.2",   "spacy-transformers==1.2.5"), pip = TRUE)
py_install(envname = "BertopicR", c(
  "bertopic==0.15.0", 
  "datasets==2.14.4",
  "tqdm==4.65.0", 
  "pytorch==2.0.0", 
  "sentence-transformers==2.2.2",
  "torchvision==0.15.2",
  "huggingface_hub==0.16.4",
  ""), method = "conda")
```
